### 2021-10-13 manuscript/ms.tex
Adding LaTeX skeleton for manuscript.

%&<latex>
\documentclass[letterpaper,12pt]{article}
\pdfoutput=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\input{../utils/environments.tex}
\input{../utils/macros.tex}
\input{../utils/notation.tex}

\newcommand{\ifdoublespacing}[2]{#1}
% \newcommand{\ifdoublespacing}[2]{#2}
\newcommand{\iflinenumbers}[2]{#1}
% \newcommand{\iflinenumbers}[2]{#2}
% \newcommand{\ifragged}[2]{#1}
\newcommand{\ifragged}[2]{#2}

\captionsetup[figure]{listformat=figList}

\usepackage[round]{natbib}
\usepackage{amsmath}
\title{The great codivergence bake off}

\author[1]{Tanner Myers}
\author[1]{Randy Klabacka}
\author[1]{Hailey Whitaker}
\author[1]{Tashitso Anamza}
\author[1]{Claire Tracy}
\author[1]{Jamie R.\ Oaks \thanks{Corresponding author: \href{mailto:joaks@auburn.edu}{\tt joaks@auburn.edu}}}
\affil[1]{Department of Biological Sciences \& Museum of Natural History, Auburn University, Auburn, Alabama 36849}

\date{\today}

\makeatletter
\let\msTitle\@title
\let\msAuthor\@author
\let\msDate\@date
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\ifragged{
\raggedright
}{}

\iflinenumbers{
\begin{linenumbers}
}{}

\textbf{Running head}: \uppercase{Codiv bake off}

{\let\newpage\relax\maketitle}

\newpage

\ifdoublespacing{
\doublespacing
}{}

\begin{abstract}
    Abstract here \ldots

    \vspace{6pt}
    \noindent\textbf{KEY WORDS:}
\end{abstract}

\newpage

\section{Introduction}

\section{Methods}

\subsection{Analyses of simulated data}

\subsection{Empirical analyses}

\section{Results}

\subsection{Analyses of simulated data}

\subsection{Empirical analyses}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/independent-div-time-scatter.pdf}
        \caption{
            \Ecoevolity estimates divergence times more accurately and precisely
            than \dppmsbayes when all five population pairs diverge independently.
        }
        \label{fig:divtimeindependent}
    \end{center}
\end{figure}

\section{Discussion}

\section{Acknowledgments}

This work was supported by funding provided to JRO from the National Science
Foundation (NSF grant number DEB 1656004).
The computational work was made possible by the Auburn University (AU) Hopper
Cluster supported by the AU Office of Information Technology
and
a grant of high-performance computing resources and technical support from the
Alabama Supercomputer Authority.
This paper is contribution number \highLight{XXX} of the Auburn University
Museum of Natural History.

%TC:ignore

\bibliographystyle{evolution}
\bibliography{references}

\iflinenumbers{
\end{linenumbers}
}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUPPORTING INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}

\captionsetup[figure]{name=Figure S, labelformat=noSpace, listformat=sFigList}
\captionsetup[table]{name=Table S, labelformat=noSpace}

\singlespacing

\section*{Supporting Information}
\hangindent=1cm
\noindent Title: \msTitle

\bigskip
{\noindent Authors: \msAuthor}

\newpage
\singlespacing

\input{si-body.tex}
\clearpage

\input{si-tables.tex}
\clearpage

\input{si-figures.tex}

%TC:endignore

\end{document}

### 2021-10-13 utils/macros.tex
Adding LaTeX skeleton for manuscript.

\newcommand{\jroedit}[2]{\sout{#1}{\color{red}{#2}}}
% \newcommand{\jroedit}[2]{#2}
\newcommand{\jrocomment}[1]{({\color{pgreen}{JRO's comment:}} \textbf{\color{pgreen}{#1}})}

\newcommand{\citationNeeded}{\textcolor{magenta}{\textbf{[CITATION NEEDED]}}\xspace}
\newcommand{\tableNeeded}{\textcolor{magenta}{\textbf{[TABLE NEEDED]}}\xspace}
\newcommand{\figureNeeded}{\textcolor{magenta}{\textbf{[FIGURE NEEDED]}}\xspace}
\newcommand{\highLight}[1]{\textcolor{magenta}{\MakeUppercase{#1}}}

\newcommand{\fig}{Figure\xspace}
\newcommand{\figs}{Figures\xspace}
\newcommand{\tbl}{Table\xspace}
\newcommand{\tbls}{Tables\xspace}

\newcommand{\datasets}{data sets\xspace}
\newcommand{\dataset}{data set\xspace}

\newcommand{\ignore}[1]{}
\newcommand{\addTail}[1]{\textit{#1}.---}
\newcommand{\super}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\sub}[1]{\ensuremath{_{\textrm{#1}}}}
\newcommand{\dC}{\ensuremath{^\circ{\textrm{C}}}}
\newcommand{\tn}{\tabularnewline}
\newcommand{\spp}[1]{\textit{#1}}

\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}

\newcommand{\change}[2]{{\color{red} #2}\xspace}
\newcommand{\thought}[1]{\textcolor{purple}{THOUGHT: #1}}

\newcommand{\widthFigure}[5]{\begin{figure}[htbp]
\begin{center}
    \includegraphics[width=#1\textwidth]{#2}
    \captionsetup{#3}
    \caption{#4}
    \label{#5}
    \end{center}
    \end{figure}}

\newcommand{\heightFigure}[5]{\begin{figure}[htbp]
\begin{center}
    \includegraphics[height=#1\textheight]{#2}
    \captionsetup{#3}
    \caption{#4}
    \label{#5}
    \end{center}
    \end{figure}}

\newcommand{\smartFigure}[5]{%
    \begin{figure}[htbp]
        \begin{center}
            \includegraphics[width=\textwidth,height=#1\textheight,keepaspectratio]{#2}
            \captionsetup{#3}
            \caption{#4}
            \label{#5}
        \end{center}
    \end{figure}
}

\newcommand{\mFigure}[4]{\smartFigure{#1}{#2}{listformat=figList}{#3}{#4}\clearpage}
\newcommand{\embedHeightFigure}[4]{\heightFigure{#1}{#2}{listformat=figList}{#3}{#4}}
\newcommand{\embedWidthFigure}[4]{\widthFigure{#1}{#2}{listformat=figList}{#3}{#4}}
\newcommand{\siFigure}[4]{\smartFigure{#1}{#2}{name=Figure S, labelformat=noSpace, listformat=sFigList}{#3}{#4}\clearpage}

%% macro to make long strings breakable over lines
\makeatletter
\def\breakable#1{\xHyphen@te#1$\unskip}
\def\xHyphen@te{\@ifnextchar${\@gobble}{\sw@p{\allowbreak{}\xHyphen@te}}}
% \def\xHyphen@te{\@ifnextchar${\@gobble}{\sw@p{\hskip 0pt plus 1pt\xHyphen@te}}}
\def\sw@p#1#2{#2#1}
\makeatother

### 2021-10-13 images/from-project-repo/update-plots-from-project-repo.sh

@@ -1,0 +1,23 @@
+#! /bin/bash
+
+set -e
+
+project_repo_path="../../../codiv-sanger-bake-off"
+
+if [ ! -e "$project_repo_path" ]
+then
+    echo "Could not find project repo:"
+    echo ""
+    echo "  $project_repo_path"
+    echo ""
+    echo "For this script to work, the 'codiv-sanger-bake-off' project repo "
+    echo "needs to be in the same directory as this ('codiv-sanger-bake-off-tex')"
+    echo "repo."
+    exit 1
+fi
+
+for plot_file in *.pdf
+do
+    project_plot_path="${project_repo_path}/results/plots/${plot_file}"
+    cp "$project_plot_path" "$plot_file"
+done

### 2024-10-03 update-plots-from-project-repo.sh
Adding script to get plots from project repo.

@@ -1,0 +1,119 @@
+#! /bin/bash
+
+set -e
+
+write_hline() {
+    echo "########################################################################"
+}
+
+write_banner_msg() {
+    echo ""
+    write_hline
+    echo "$@"
+    write_hline
+}
+
+# Display help info
+usage () {
+echo ""
+echo "Usage:"
+echo "  $0 [ OPTIONS ] [ GIT-REF ]"
+echo ""
+echo "Example:"
+echo ""
+echo "  $0 HEAD"
+echo ""
+echo "Optional flag arguments ( 'OPTIONS' ):"
+echo "  -h|--help         Show help message and exit."
+echo ""
+echo "Positional arguments ( 'GIT-REF' ):"
+echo "  The Git ref for the codiv backoff project repo. Plots from this commit"
+echo "  will be copied into this manuscript repo."
+echo "  If no ref is provided, the default is to use the most recent commit of"
+echo "  of the project repo."
+echo ""
+}
+
+this_dir="$( cd -P "$( dirname "${BASH_SOURCE[0]}" )" >/dev/null 2>&1 && pwd )"
+
+# Remove the temporary directory created for project repo
+clean_up() {
+  test -d "$tmp_dir" && rm -rf "${tmp_dir}/.git" && rm -r "$tmp_dir"
+}
+# Ensure temp dir gets deleted on exit
+trap clean_up EXIT
+# Make temp dir for cloning project repo 
+# The or ("||") syntax is to support different flavors of `mktemp`; Darwin's
+# mktemp behaves differently than Gnu's.
+tmp_dir="$(mktemp -d 2>/dev/null || mktemp -d -t 'tmp_codiv_bakeoff')"
+
+project_dir="$tmp_dir"
+
+project_plot_dir="${project_dir}/results/plots"
+project_emp_plot_dir="${project_dir}/results/empirical-plots"
+image_dir="${this_dir}/images"
+if [ ! -d "$image_dir" ]
+then
+    mkdir "$image_dir"
+fi
+dest_dir="${image_dir}/from-project-repo"
+if [ ! -d "$dest_dir" ]
+then
+    mkdir "$dest_dir"
+fi
+
+
+###############################################################################
+# Process command line args
+
+positional_args=()
+
+while [ -n "$1" ]
+do
+    case $1 in
+        -h | --help)
+            usage
+            exit
+            ;;
+        -* | --*)
+            echo "Unrecognized option flag: \"$1\""
+            usage
+            exit 1
+            ;;
[…]

### 2024-10-03 images/from-project-repo/update-plots-from-project-repo.sh
Removing old plots and plot script.

@@ -1,23 +1,0 @@
-#! /bin/bash
-
-set -e
-
-project_repo_path="../../../codiv-sanger-bake-off"
-
-if [ ! -e "$project_repo_path" ]
-then
-    echo "Could not find project repo:"
-    echo ""
-    echo "  $project_repo_path"
-    echo ""
-    echo "For this script to work, the 'codiv-sanger-bake-off' project repo "
-    echo "needs to be in the same directory as this ('codiv-sanger-bake-off-tex')"
-    echo "repo."
-    exit 1
-fi
-
-for plot_file in *.pdf
-do
-    project_plot_path="${project_repo_path}/results/plots/${plot_file}"
-    cp "$project_plot_path" "$plot_file"
-done

### 2024-10-04 manuscript/ms.tex
Working on adding results to manuscript.

@@
 
-\subsection{Analyses of simulated data}
-
-\subsection{Empirical analyses}
+\subsection{Simulation results}
 
@@
     \begin{center}
-        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/independent-div-time-scatter.pdf}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-model-distance-cropped.pdf}
         \caption{
-            \Ecoevolity estimates divergence times more accurately and precisely
-            than \dppmsbayes when all five population pairs diverge independently.
+            \Ecoevolity estimates the partitioning of population pairs to
+            divergence times (the divergence model) more accurately and
+            precisely than \dppmsbayes across all simulated numbers of loci
+            (columns) and whether the divergence model was drawn from a
+            Dirichlet process (top row), or constrained so that all pairs of
+            populations diverged independently (middle row) or simultaneously
+            (bottom row).
+            Divergence model estimation error was quantified for each
+            simulation replicate using the mean partition distance
+            \citep{Regnier1983,Gusfield2002} between the true divergence model
+            and the posterior samples of divergence models.
+            Partition distances was calculated using the Hungarian (or
+            Kuhn-Munkres) algorithm
+            \citep{Kuhn1955,Munkres1957}
+            as implemented in \pycoevolity
+            \citep[Version 0.2.11 Commit 85ea44b;][]{Oaks2018ecoevolity,PycoevolityRepoOnline},
+            which relies on the Munkres Python package
+            \citep[Version 1.1.4;][]{Clapper2020}.
+            For each violin plot, the sample size (number of simulation
+            replicates) is shown beneath and the mean is represented by the
+            white dot and shown above.
+            The box shows the upper and lower quartiles and the brackets
+            show the 2.5th and 97.5th percentiles.
+            At the top center of each plot, the results of a Mann-Whitney U
+            test \citep{MannWhitney1947} are shown comparing mean model errors
+            between \ecoevolity and \dppmsbayes;
+            the probability of superiority \citep[PoS, the probability that
+            \ecoevolity has a lower mean model error than \dppmsbayes for a
+            random simulation replicate drawn from
+            each;][]{WolfeHogg1971,Grissom1994} and p-value is provided.
         }
-        \label{fig:divtimeindependent}
+        \label{fig:modelerror}
     \end{center}
 \end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-div-time-error-cropped.pdf}
+        \caption{
+            \Ecoevolity better estimates divergence times than \dppmsbayes
+            across all simulated numbers of loci (columns) and whether the
+            divergence model was drawn from a Dirichlet process (top row), or
+            constrained so that all pairs of populations diverged independently
+            (middle row) or simultaneously (bottom row).
+            Divergence time error was quantified for each simulation replicate
+            as the sum of the difference between the true and posterior mean
+            divergence time across the five pairs of populations.
+            For each violin plot, the sample size (number of simulation
+            replicates) is shown beneath and the mean is represented by the
+            white dot and shown above.
+            The box shows the upper and lower quartiles and the brackets
+            show the 2.5th and 97.5th percentiles.
+            At the top center of each plot, the results of a Mann-Whitney U
+            test \citep{MannWhitney1947} are shown comparing mean model errors
+            between \ecoevolity and \dppmsbayes;
+            the probability of superiority \citep[PoS, the probability that
+            \ecoevolity has a lower mean model error than \dppmsbayes for a
+            random simulation replicate drawn from
+            each;][]{WolfeHogg1971,Grissom1994} and p-value is provided.
+        }
+        \label{fig:divtimeerror}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/plots/free-div-time-scatter-cropped.pdf}
+        \caption{
+            \Ecoevolity (top row) estimates divergence times more accurately
+            and precisely than \dppmsbayes (bottom row) across all simulated
+            numbers of loci (columns) for five pairs of populations simulated
+            to have diverged according to a Dirichlet process.
+            Each plotted circle and associated error bars represent the posterior mean
+            and 95\% credible interval.
+            \accuracyscatterplotannotations{\comparisonetime{}}
+        }
+        \label{fig:divtimeerrordp}
+    \end{center}
+\end{figure}
+
+\subsection{Empirical results}
 
@@
 The computational work was made possible by the Auburn University (AU) Hopper
-Cluster supported by the AU Office of Information Technology
-and
-a grant of high-performance computing resources and technical support from the
-Alabama Supercomputer Authority.
+Cluster supported by the AU Office of Information Technology and a grant of
+high-performance computing resources and technical support from the Alabama
+Supercomputer Authority.
 This paper is contribution number \highLight{XXX} of the Auburn University

### 2024-10-04 manuscript/si-figures.tex
Working on adding results to manuscript.

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-nevents-cropped.pdf}
        \caption{
            \scriptsize
            \Ecoevolity better estimates the number of divergence
            events than \dppmsbayes across all simulated numbers of
            loci (columns) for five pairs of populations simulated to have
            diverged according to a Dirichlet process (top 8 plots),
            indepedently (middle 8 plots),
            or
            simultaneously (bottom 8 plots).
            \neventsshadingdescription{}
            \neventsplotannotations{}
        }
        \label{fig:neventsdp}
    \end{center}
\end{figure}

\clearpage

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-ancestral-pop-size-error-cropped.pdf}
        \caption{
            \scriptsize
            \Ecoevolity better estimates the effective size of the ancestral
            populations than \dppmsbayes across all simulated numbers of loci
            (columns) and whether the divergence model was drawn from a
            Dirichlet process (top row), or constrained so that all pairs of
            populations diverged independently (middle row) or simultaneously
            (bottom row).
            Error was quantified for each simulation replicate
            as the sum of the difference between the true and posterior mean
            population size across the five pairs of populations.
            For each violin plot, the sample size (number of simulation
            replicates) is shown beneath and the mean is represented by the
            white dot and shown above.
            The box shows the upper and lower quartiles and the brackets
            show the 2.5th and 97.5th percentiles.
            At the top center of each plot, the results of a Mann-Whitney U
            test \citep{MannWhitney1947} are shown comparing mean model errors
            between \ecoevolity and \dppmsbayes;
            the probability of superiority \citep[PoS, the probability that
            \ecoevolity has a lower mean model error than \dppmsbayes for a
            random simulation replicate drawn from
            each;][]{WolfeHogg1971,Grissom1994} and p-value is provided.
        }
        \label{fig:ancpopsizeerror}
    \end{center}
\end{figure}

\clearpage

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-div-time-scatter-cropped.pdf}
        \caption{
            \scriptsize
            \Ecoevolity estimates divergence times more accurately
            and precisely than \dppmsbayes across all simulated
            numbers of loci (columns) for five pairs of populations simulated
            to have diverged according to a dirichlet process (top 8 plots),
            independently (middle 8 plots),
            or simultaneously (bottom 8 plots).
            Each plotted circle and associated error bars represent the posterior mean
            and 95\% credible interval.
            \accuracyscatterplotannotations{\comparisonetime{}}
        }
        \label{fig:divtimescatterindependent}
    \end{center}
\end{figure}

\clearpage

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-leaf-pop-size-scatter-cropped.pdf}
        \caption{
            \scriptsize
            \Ecoevolity estimates the effective sizes of the
            descendant populations more accurately and precisely than
            \dppmsbayes across all simulated numbers of loci
            (columns) for five pairs of populations simulated to have diverged
            according to a Dirichlet process (top 8 plots),
            independently (middle 8 plots),
            or simultaneously (bottom 8 plots).
            Each plotted circle and associated error bars represent the posterior mean
            and 95\% credible interval.
            \accuracyscatterplotannotations{\epopsize{}}
        }
        \label{fig:leafpopsizescatterdp}
    \end{center}
\end{figure}

\clearpage

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-root-pop-size-scatter-cropped.pdf}
        \caption{
            \Ecoevolity estimates the effective sizes of the
            ancestral populations more accurately and precisely than
            \dppmsbayes across all simulated numbers of loci
            (columns) for five pairs of populations simulated to have diverged
            according to a Dirichlet process (top 8 plots),
            independently (middle 8 plots),
            or simultaneously (bottom 8 plots).
            Each plotted circle and associated error bars represent the posterior mean
            and 95\% credible interval.
            \accuracyscatterplotannotations{\epopsize{}}
        }
        \label{fig:rootpopsizescatterdp}
    \end{center}
\end{figure}

### 2024-10-04 utils/macros.tex
Working on adding results to manuscript.

@@
 \makeatother
+
+\newcommand{\accuracyscatterplotannotations}[1]{For each plot, the
+    root-mean-square error (RMSE) and the proportion of estimates for which the
+    95\% credible interval contained the true value---$p(#1 \in
+    \textrm{CI})$---is given.
+}
+\newcommand{\neventsplotannotations}{For each plot,
+    the proportion of simulation replicates for which the number of events with
+    the largest posterior probability matched the true number of
+    events---$p(\hat{\nevents} = \nevents)$---is shown in the upper left
+    corner,
+    the median posterior probability of the correct number of events across all
+    simulations---$\widetilde{p(\nevents|\alldata)}$---is shown in the upper
+    right corner, and
+    the proportion of simulations for which the true divergence model was
+    included in the 95\% credible set---$p(\nevents \in
+    \textrm{CS})$---is shown in the lower right.
+}
+\newcommand{\neventsbarplotannotations}{For each plot, the following summary
+    statistics are shown:
+    the proportion of simulation replicates for which the number of events with
+    the largest posterior probability matched the true number of
+    events---$p(\hat{\nevents} = \nevents)$---,
+    the median posterior probability of the correct number of events across all
+    simulations---$\widetilde{p(\nevents|\alldata)}$---, and
+    the proportion of simulations for which the true divergence model was
+    included in the 95\% credible set---$p(\nevents \in
+    \textrm{CS})$---.
+}
+\newcommand{\neventsshadingdescription}{The number of simulation replicates
+    that fall within each possible cell of true versus estimated numbers of
+    events is shown, and cells with more replicates are shaded darker.
+}

### 2024-10-04 update-plots-from-project-repo.sh

@@ -112,6 +112,12 @@ write_banner_msg "Checking out commit $commit_sha  of bakeoff project repo..."
 (
     cd "$project_dir"
     git checkout -b tmp "$commit_sha"
+    git lfs pull --include "*.pdf"
+    files_to_remove=$(find results/plots -type f ! -name "*.pdf" && find results/empirical-plots -type f ! -name "*.pdf")
+    for f in $files_to_remove
+    do
+        rm "$f"
+    done
 )
 
 write_banner_msg "Copying plot directories from project repo..."

### 2024-10-08 manuscript/ms.tex
Working on methods and results.

@@
 
+We simulated loci for 5 diploid individuals (i.e., 10 gene
+copies) per population from 5 pairs of diverging populations.
+Each pair shared a common ancestral population with a constant effective size
+\epopsize[\rootpopindex]
+that diverged at time
+\comparisonetime{}
+into two descendant populations with constant effective sizes
+\epopsize[\descendantpopindex{1}]
+and 
+\epopsize[\descendantpopindex{2}].
+Each locus we simulated comprised 500 linked characters with no intralocus
+recombination.
+We simulated datasets comprising 1, 2, 5, and 20 independent loci.
+For each number of loci, we simulated datasets under three divergence
+scenarios:
+\begin{enumerate}
+    \item All five pairs of populations diverged independently.
+    \item All five pairs of populations diverged simultaneously.
+    \item The number of divergence times (\nevents) and the assignment of the
+        five pairs of populations to the divergene times (\divtimesets) vary
+        according to a Dirichlet-process model with a concentration parameter
+        of 2.22543.
+\end{enumerate}
+For each of the 12 simulation conditions (4 numbers of loci $\times$ 3
+divergence scenarios),
+we simulated 1000 datasets.
+Each unique divergence time was drawn from an exponential distribution,
+$\comparisonetime \sim \dexponential{0.01}$.
+We constrained the mutation rate (\murate{}) to 1 across the five pairs of
+populations, such that divergence times and effective population sizes were
+scaled by the mutation rate.
+
+\subsubsection{Full-likelihood analyses}
+
+To simulate datasets and analyze them under a full-likelihood Bayesian model of
+population divergences, we used the \simcoevolity and \ecoevolity tools of the
+\ecoevolity software package
+\citep[Version 0.3.2, Commit c128046;][]{Oaks2018ecoevolity,Oaks2018paic}.
+
+The mutation-scaled effective sizes of the descendant populations
+($\epopsize\murate$) were drawn from a gamma distribution with a shape of 10
+and mean of 0.0005,
+$\epopsize{}\murate{} \sim \dgamma{10}{0.0005}$.
+The effective size of the ancestral population relative to the mean of
+its descendants was drawn from a gamma distribution with a shape of 40 and mean of 1,
+$\rootrelativepopsize \sim \dgamma{40}{1.0}$.
+
+When analyzing each simulated \dataset with \ecoevolity, we ran four MCMC
+chains for 30,000 generations sampling every 20 generations.
+We used the last 1000 samples from each of the four chains to approximate the
+posterior distribution of the model given each simulated dataset.
+To assess convergence and mixing of the MCMC chains, we calculated the
+potential scale reduction factor \citep[PSRF; the square root of Equation 1.1
+in][]{Brooks1998} and effective sample size \citep[ESS;][]{Gong2014} for all
+continuous parameters and the log likelihood using
+\pycoevolity
+\citep[Version 0.2.11 Commit 85ea44b;][]{Oaks2018ecoevolity,PycoevolityRepoOnline}.
+% When plotting results, we highlight any simulation replicates that have a
+% $\textrm{PSRF} > 1.2$.
+
+\subsubsection{ABC analyses}
+
+To simulate datasets and analyze them under a similar model estimated via
+approximate-Bayesian computation (ABC),
+we used \pymsbayes
+\citep[Version 0.3.7, Commit 54f720df;][]{Oaks2014dpp},
+which is a Python multiprocessing wrapper around dpp-msbayes
+\citep{Oaks2014dpp}, which is a modification of
+MTML-msBayes \citep{Huang2011}.
+In this software, the distribution for effective population sizes is placed
+on the parameter $4\epopsize{}\murate{}$, for which we used
+a gamma distribution with a shape of 10 and a mean of 0.002.
+Note, this is equivalent to the distribution we used for $\epopsize{}\murate{}$
+in \ecoevolity.
+
 \subsection{Empirical analyses}
@@
 \subsection{Simulation results}
+
+The potential scale reduction facter (PSRF) was less than X and the effective
+sample size (ESS) was greater than Y for all parameters and the log likelihood
+across all simulations
+(Fig.\ S\labelcref{fig:psrfdivtime,fig:psrfrootpopsize,fig:psrflnl,fig:essdivtime,fig:essrootpopsize,fig:esslnl}).
 

### 2024-10-08 manuscript/si-figures.tex
Working on methods and results.

@@
 \end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-psrf-div-time-histograms-cropped.pdf}
+        \caption{
+            The potential scale reduction factor \citep[PSRF; the square root
+            of Equation 1.1 in][]{Brooks1998}
+            for the divergence time parameter calculated from the last 1000
+            samples of the four MCMC chains run for each simulation replicate.
+            The mean PSRF across the 1000 simulation replicates is shown at the
+            top right of each plot, followed by the range in parentheses.
+        }
+        \label{fig:psrfdivtime}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-psrf-root-pop-size-histograms-cropped.pdf}
+        \caption{
+            The potential scale reduction factor \citep[PSRF; the square root
+            of Equation 1.1 in][]{Brooks1998}
+            for the ancestral population size calculated from the last 1000
+            samples of the four MCMC chains run for each simulation replicate.
+            The mean PSRF across the 1000 simulation replicates is shown at the
+            top right of each plot, followed by the range in parentheses.
+        }
+        \label{fig:psrfrootpopsize}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-psrf-lnl-histograms-cropped.pdf}
+        \caption{
+            The potential scale reduction factor \citep[PSRF; the square root
+            of Equation 1.1 in][]{Brooks1998}
+            for the log likelihood calculated from the last 1000
+            samples of the four MCMC chains run for each simulation replicate.
+            The mean PSRF across the 1000 simulation replicates is shown at the
+            top right of each plot, followed by the range in parentheses.
+        }
+        \label{fig:psrflnl}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-ess-div-time-histograms-cropped.pdf}
+        \caption{
+            The effective sample size \citep[ESS;][]{Gong2014} for the
+            divergence time parameter calculated from the last 1000 samples of
+            the four MCMC chains run for each simulation replicate.
+            The mean ESS across the 1000 simulation replicates is shown at the
+            top right of each plot, followed by the range in parentheses.
+        }
+        \label{fig:essdivtime}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-ess-root-pop-size-histograms-cropped.pdf}
+        \caption{
+            The effective sample size \citep[ESS;][]{Gong2014} for the
+            ancestral population size calculated from the last 1000 samples of
+            the four MCMC chains run for each simulation replicate.
+            The mean ESS across the 1000 simulation replicates is shown at the
+            top right of each plot, followed by the range in parentheses.
+        }
+        \label{fig:essrootpopsize}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/plots/tex-plot-grids/grid-ess-lnl-histograms-cropped.pdf}
+        \caption{
+            The effective sample size \citep[ESS;][]{Gong2014} for the
+            log likelihood calculated from the last 1000 samples of
+            the four MCMC chains run for each simulation replicate.
+            The mean ESS across the 1000 simulation replicates is shown at the
+            top right of each plot, followed by the range in parentheses.
+        }
+        \label{fig:esslnl}
+    \end{center}
+\end{figure}

### 2024-10-08 manuscript/ms.tex
Working on method and results.

@@
 
-\subsection{Analyses of simulated data}
+\subsection{Simulating data}
 
@@
     \item The number of divergence times (\nevents) and the assignment of the
-        five pairs of populations to the divergene times (\divtimesets) vary
+        five pairs of populations to the divergene times (\etimesets) vary
         according to a Dirichlet-process model with a concentration parameter
@@
 
-\subsubsection{Full-likelihood analyses}
-
-To simulate datasets and analyze them under a full-likelihood Bayesian model of
-population divergences, we used the \simcoevolity and \ecoevolity tools of the
-\ecoevolity software package
+To simulate the datasets for analysis under a full-likelihood Bayesian model,
+we used the \simcoevolity tool of the \ecoevolity software package.
 \citep[Version 0.3.2, Commit c128046;][]{Oaks2018ecoevolity,Oaks2018paic}.
-
 The mutation-scaled effective sizes of the descendant populations
@@
 
-When analyzing each simulated \dataset with \ecoevolity, we ran four MCMC
-chains for 30,000 generations sampling every 20 generations.
-We used the last 1000 samples from each of the four chains to approximate the
-posterior distribution of the model given each simulated dataset.
-To assess convergence and mixing of the MCMC chains, we calculated the
-potential scale reduction factor \citep[PSRF; the square root of Equation 1.1
-in][]{Brooks1998} and effective sample size \citep[ESS;][]{Gong2014} for all
-continuous parameters and the log likelihood using
-\pycoevolity
-\citep[Version 0.2.11 Commit 85ea44b;][]{Oaks2018ecoevolity,PycoevolityRepoOnline}.
-% When plotting results, we highlight any simulation replicates that have a
-% $\textrm{PSRF} > 1.2$.
-
-\subsubsection{ABC analyses}
-
-To simulate datasets and analyze them under a similar model estimated via
+To simulate datasetsfor analysis with
 approximate-Bayesian computation (ABC),
@@
 a gamma distribution with a shape of 10 and a mean of 0.002.
-Note, this is equivalent to the distribution we used for $\epopsize{}\murate{}$
-in \ecoevolity.
+This is equivalent to the distribution we used for $\epopsize{}\murate{}$ with
+\ecoevolity.
+When summarizing and plotting effective population size for \pymsbayes, we
+divided all true and estimated values by four for direct comparability with
+\ecoevolity.
 
-\subsection{Empirical analyses}
+\subsection{Full-likelihood analyses of simulated data}
+
+We analyzed each dataset simulated by \simcoevolity with \ecoeovlity 
+\citep[Version 0.3.2, Commit c128046;][]{Oaks2018ecoevolity,Oaks2018paic}
+under a Dirichlet-process model with a concentration parameter of 2.22543.
+For prior distributions on divergence times and effective population sizes, we
+used the same distributions described above for the simulations.
+We ran four MCMC chains for 30,000 generations sampling every 20 generations.
+To approximate the posterior distribution of the model given each simulated
+dataset, we used the last 1000 samples from each of the four chains.
+To assess convergence and mixing of the MCMC chains, we calculated the
+potential scale reduction factor \citep[PSRF; the square root of Equation 1.1
+in][]{Brooks1998} and effective sample size \citep[ESS;][]{Gong2014} for all
+continuous parameters and the log likelihood using
+\pycoevolity
+\citep[Version 0.2.11 Commit 85ea44b;][]{Oaks2018ecoevolity,PycoevolityRepoOnline}.
+
+\subsubsection{ABC analyses of simulated data}
+
+To analyze each dataset simulated by \pymsbayes, we used the ABC rejection
+algorithm implemented in dpp-msbayes via \pymsbayes \citep[Version 0.3.7,
+Commit 54f720df;][]{Oaks2014dpp},
+under a Dirichlet-process model with a concentration parameter of 2.22543, and
+prior distributions on divergence times and effective populatoin sizes that
+match the simulation distributions described above.
+We simulated 1 million samples to approximate the joint prior distribution of
+the model.
+To approximate the posterior given each simulated dataset, we retained the 2000
+prior samples with the smallest Euclidean distance for four summary statistics
+standardized using the mean and standard deviation from the prior sample
+\citep{Oaks2014dpp}:
+$\pi$ \cite{Tajima1983}, $\theta_W$ \cite{Watterson1975}, $\pi_{net}$
+\cite{Takahata1985}, and $SD(\pi-\theta_W)$ \cite{Tajima1989}.
+
+\subsection{Analyses of biological data}
 
@@
 
-The potential scale reduction facter (PSRF) was less than X and the effective
-sample size (ESS) was greater than Y for all parameters and the log likelihood
-across all simulations
+The potential scale reduction facter (PSRF) was less than 1.01 and the
+effective sample size (ESS) was greater than 600 for all parameters and the log
+likelihood across all simulations
 (Fig.\ S\labelcref{fig:psrfdivtime,fig:psrfrootpopsize,fig:psrflnl,fig:essdivtime,fig:essrootpopsize,fig:esslnl}).

### 2024-11-20 manuscript/ms.tex
Fixing typo that was preventing latex from compiling.
Mostly working on empirical methods and results.
Also making edits to simulation methods and results.

@@
 
-We simulated loci for 5 diploid individuals (i.e., 10 gene
-copies) per population from 5 pairs of diverging populations.
+We simulated loci for five diploid individuals (i.e., 10 gene
+copies) per population from five pairs of diverging populations.
 Each pair shared a common ancestral population with a constant effective size
@@
     \item The number of divergence times (\nevents) and the assignment of the
-        five pairs of populations to the divergene times (\etimesets) vary
+        five pairs of populations to the divergence times (\etimesets) vary
         according to a Dirichlet-process model with a concentration parameter
-        of 2.22543.
+        of 2.22543, which corresponds to a mean of 3 divergence times.
 \end{enumerate}
@@
 
-To simulate datasetsfor analysis with
+To simulate datasets for analysis with
 approximate-Bayesian computation (ABC),
@@
 \citep[Version 0.3.7, Commit 54f720df;][]{Oaks2014dpp},
-which is a Python multiprocessing wrapper around dpp-msbayes
+which is a Python multiprocessing wrapper around \dppmsbayes
 \citep{Oaks2014dpp}, which is a modification of
@@
 
-We analyzed each dataset simulated by \simcoevolity with \ecoeovlity 
+We analyzed each dataset simulated by \simcoevolity with \ecoevolity
 \citep[Version 0.3.2, Commit c128046;][]{Oaks2018ecoevolity,Oaks2018paic}
@@
 To analyze each dataset simulated by \pymsbayes, we used the ABC rejection
-algorithm implemented in dpp-msbayes via \pymsbayes \citep[Version 0.3.7,
+algorithm implemented in \dppmsbayes via \pymsbayes \citep[Version 0.3.7,
 Commit 54f720df;][]{Oaks2014dpp},
 under a Dirichlet-process model with a concentration parameter of 2.22543, and
-prior distributions on divergence times and effective populatoin sizes that
+prior distributions on divergence times and effective population sizes that
 match the simulation distributions described above.
@@
 To approximate the posterior given each simulated dataset, we retained the 2000
-prior samples with the smallest Euclidean distance for four summary statistics
-standardized using the mean and standard deviation from the prior sample
+prior samples with the smallest Euclidean distance for the following four
+summary statistics standardized using the mean and standard deviation from the
+prior sample
 \citep{Oaks2014dpp}:
@@
 
-\subsection{Analyses of biological data}
+\subsection{Re-analyses of biological data}
+
+To assess the effect of a using a full-likelihood approach, we reanalyzed two
+datasets with previously published results of using the ABC approach to
+estimating shared divergence times.
+
+In their study into the factors affecting the divergence of flightless darkling
+beetles across the Aegean Archipelago,
+Papadopoulou and Knowles \citeyear{PapadopoulouKnowles2015} used \dppmsbayes to
+estimate the relative divergence times of 13 pairs of populations.
+\jrocomment{We should probably describe the dataset a bit; number of loci, etc.}
+
+To test the prediction of clustered divergences driven by Pleistocene glacial
+cycles Oaks et al.\ \citeyear{Oaks2012} used MTML-msBayes \cite{Huang2011} to
+estimate the divergence times of 22 pairs of populations from across the
+Philippine Islands.
+Oaks \citeyear{Oaks2014dpp} reanalyzed these same data using \dppmsbayes.
+\jrocomment{We should probably describe the dataset a bit; number of loci, etc.}
+
+\jrocomment{Jamie needs to add analysis details here}.
 
@@
 
-The potential scale reduction facter (PSRF) was less than 1.01 and the
+We found good convergence and mixing of the MCMC chains across the \ecoevolity
+analyses of the 12,000 simulated dataset.
+The potential scale reduction factor (PSRF) was less than 1.01 and the
 effective sample size (ESS) was greater than 600 for all parameters and the log
 likelihood across all simulations
-(Fig.\ S\labelcref{fig:psrfdivtime,fig:psrfrootpopsize,fig:psrflnl,fig:essdivtime,fig:essrootpopsize,fig:esslnl}).
+(\figs S\labelcref{fig:psrfdivtime,fig:psrfrootpopsize,fig:psrflnl,fig:essdivtime,fig:essrootpopsize,fig:esslnl}).
+
+Across all four numbers of loci and three divergence scenarios, \ecoevolity
+performed better at estimating the divergence model (\ie, the number of
+divergence times and the assignment of the five pairs of populations to those
+divergences) than \dppmsbayes, and the differences were significant according
+to a Mann-Whitney U test \citep[\fig~\ref{fig:modelerror};][]{MannWhitney1947}.
+The better performance of \ecoevolity is small when there is only one 500-base
+locus, but the performance difference increases as the number of loci increase.
+This is largely due to the fact that the ABC method (\dppmsbayes) does not gain
+much information from additional loci, whereas the full-likelihood method
+(\ecoevolity) does (\fig~\ref{fig:modelerror}).
+The same pattern is true when looking at estimation error of divergence times
+(\figs \ref{fig:divtimeerror}, \ref{fig:divtimescatterdp}, \& S\ref{fig:divtimescatter}),
+the number of divergence times
+(\fig S\ref{fig:nevents}),
+and the effective population sizes 
+(\figs S\labelcref{fig:ancpopsizeerror,fig:leafpopsizescatter,fig:rootpopsizescatter}).
 
@@
         }
-        \label{fig:divtimeerrordp}
+        \label{fig:divtimescatterdp}
     \end{center}
@@
 \subsection{Empirical results}
+
+\jrocomment{For now I am just dropping plots below.}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-all-pairs/pyco-sumevents-mediterranean-all-pairs-pycoevolity-nevents-cropped.pdf}
+        \caption{
+            \Ecoevolity results for all Mediterranean pairs.
+        }
+        \label{fig:neventsmediall}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-soil-pairs/pyco-sumevents-mediterranean-soil-pairs-pycoevolity-nevents-cropped.pdf}
+        \caption{
+            \Ecoevolity results for soil Mediterranean pairs.
+        }
+        \label{fig:neventsmedisoil}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-all-pairs/pyco-sumevents-philippines-all-pairs-pycoevolity-nevents-cropped.pdf}
+        \caption{
+            \Ecoevolity results for all Philippines pairs.
+        }
+        \label{fig:neventsphilall}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-negros-panay-pairs/pyco-sumevents-philippines-negros-panay-pairs-pycoevolity-nevents-cropped.pdf}
+        \caption{
+            \Ecoevolity results for Negros-Panay pairs.
+        }
+        \label{fig:neventsphilnp}
+    \end{center}
+\end{figure}
 

### 2024-12-05 manuscript/ms.tex
Adding some temporary page breaks.
Adding page breaks to make sections in PDF easier to delineate.
Adding information about empirical datasets in Methods

@@
 
-\author[1]{Tanner Myers}
+\author[1]{Tanner C.\ Myers}
 \author[1]{Randy Klabacka}
@@
 datasets with previously published results of using the ABC approach to
-estimating shared divergence times.
+estimate shared divergence times.
 
-In their study into the factors affecting the divergence of flightless darkling
-beetles across the Aegean Archipelago,
-Papadopoulou and Knowles \citeyear{PapadopoulouKnowles2015} used \dppmsbayes to
-estimate the relative divergence times of 13 pairs of populations.
+In their study into the factors affecting the divergence of flightless darkling beetles across the Aegean Archipelago,
+Papadopoulou and Knowles \citeyear{PapadopoulouKnowles2015} used \dppmsbayes to estimate the relative divergence times of 13 pairs of populations that vary phenotypically and ecologically.
+Their dataset included two Sanger loci --- one mitochondrial (Cox1; \textit{n} = 403) and one nuclear (Mp20; \textit{n} = 273)--- sequenced across hundreds of beetles from 60 localities on the 11 islands on the Cycladic plateau in the Aegean archipelago \citep{PapadopoulouKnowles2015}.
 \jrocomment{We should probably describe the dataset a bit; number of loci, etc.}
@@
 To test the prediction of clustered divergences driven by Pleistocene glacial
-cycles Oaks et al.\ \citeyear{Oaks2012} used MTML-msBayes \cite{Huang2011} to
-estimate the divergence times of 22 pairs of populations from across the
+cycles Oaks et al.\ \citeyear{Oaks2012} used MTML-msBayes \citep{Huang2011} to
+estimate the divergence times of 22 pairs of vertebrate populations from across the
 Philippine Islands.
 Oaks \citeyear{Oaks2014dpp} reanalyzed these same data using \dppmsbayes.
+This dataset consists of one or two mitochondrial loci gathered from closely related species or populations within species distributed across contemporarily isolated islands that previous were contiguous.
 \jrocomment{We should probably describe the dataset a bit; number of loci, etc.}
@@
 
+% We can remove this page break later, just adding it now to make it easier to
+% delineate empirical results in the PDF
+\newpage
+
 \subsection{Empirical results}
@@
 \end{figure}
+
+% We can remove this page break later, just adding it now to make it easier to
+% delineate empirical results in the PDF
+\newpage
 

### 2024-12-11 manuscript/ms.tex
Accepted track changes on Overleaf

@@
 Papadopoulou and Knowles \citeyear{PapadopoulouKnowles2015} used \dppmsbayes to estimate the relative divergence times of 13 pairs of populations that vary phenotypically and ecologically.
-Their dataset included two Sanger loci --- one mitochondrial (Cox1; \textit{n} = 403) and one nuclear (Mp20; \textit{n} = 273)--- sequenced across hundreds of beetles from 60 localities on the 11 islands on the Cycladic plateau in the Aegean archipelago \citep{PapadopoulouKnowles2015}.
+Their dataset included two Sanger loci --- one mitochondrial (Cox1; \textit{n} = 403) and one nuclear (Mp20; \textit{n} = 273)--- sequenced across hundreds of beetles from 60 localities on 11 islands of the Cycladic plateau in the Aegean archipelago \citep{PapadopoulouKnowles2015}.
 \jrocomment{We should probably describe the dataset a bit; number of loci, etc.}

### 2025-11-26 update-plots-from-project-repo.sh
Working on script to update plots.

@@ -36,6 +36,8 @@ echo ""
 
 this_dir="$( cd -P "$( dirname "${BASH_SOURCE[0]}" )" >/dev/null 2>&1 && pwd )"
 
+sister_project_dir="$(dirname "$this_dir")/codiv-sanger-bake-off"
+
 # Remove the temporary directory created for project repo
 clean_up() {
   test -d "$tmp_dir" && rm -rf "${tmp_dir}/.git" && rm -r "$tmp_dir"
@@ -46,21 +48,6 @@ trap clean_up EXIT
 # The or ("||") syntax is to support different flavors of `mktemp`; Darwin's
 # mktemp behaves differently than Gnu's.
 tmp_dir="$(mktemp -d 2>/dev/null || mktemp -d -t 'tmp_codiv_bakeoff')"
-
-project_dir="$tmp_dir"
-
-project_plot_dir="${project_dir}/results/plots"
-project_emp_plot_dir="${project_dir}/results/empirical-plots"
-image_dir="${this_dir}/images"
-if [ ! -d "$image_dir" ]
-then
-    mkdir "$image_dir"
-fi
-dest_dir="${image_dir}/from-project-repo"
-if [ ! -d "$dest_dir" ]
-then
-    mkdir "$dest_dir"
-fi
 
 
 ###############################################################################
@@ -96,29 +83,67 @@ then
     exit 1
 fi
 
-write_banner_msg "Cloning codiv bakeoff project repo..."
-git clone git@github.com:phyletica/codiv-sanger-bake-off.git "$project_dir"
-
-git_ref="$(cd "$project_dir"; git rev-parse --short HEAD)"
-if [ "${#positional_args[@]}" = "1" ]
+using_git=true
+if [ -d "$sister_project_dir" ]
 then
-    git_ref="${positional_args[0]}"
+    using_git=false
 fi
 
-commit_sha="$(cd "$project_dir"; git rev-parse --short "$git_ref")"
+if [ "${#positional_args[@]}" = "1" ]
+then
+    using_git=true
+fi
 
-# Make sure we are on the correct commit so we copy the correct images
-write_banner_msg "Checking out commit $commit_sha  of bakeoff project repo..."
-(
-    cd "$project_dir"
-    git checkout -b tmp "$commit_sha"
-    git lfs pull --include "*.pdf"
[…]

### 2025-11-26 manuscript/ms.tex
Working on manuscript.
Sketching out an introduction and adding some text about
the nature of the simulations.

@@
 
+To understand the distribution of biodiversity, the field of historical
+biogeography considers how past environmental changes have shaped diversity
+within and among species.
+Environmental processes that affect whole biological communities can cause
+speciation or extinction across multiple species at the same time.
+Biogeographers are often interested in testing for patterns of temporally
+clustered speciation events as evidence that a shared process caused multiple
+lineages to diverge.
+For example, finding that a number of evolutionary lineages diverged
+simultaneously can be difficult to explain via species-specific processes alone and
+provides compelling evidence for a shared process of diversification, like the
+fragmentation of an environment.
+
+One way to test the predictions of such processes of diversification is to
+infer the temporal pattern of divergences across multiple taxa, and determine
+whether any subsets of the taxa shared the same divergence times.
+Methods have been developed to test for such patterns of shared divergence
+times across taxa using approximate Bayesian computation (ABC)
+\citep{Hickerson2006,Huang2011,Oaks2014dpp}
+and likelihood-based Bayesian inference
+\citep{Oaks2018ecoevolity,Oaks2019codemog}.
+Both approaches use Bayesian model choice to infer the temporal pattern of
+divergences across multiple pairs of populations or species.
+
+Several of the ABC methods were primarily developed for analyzing a small
+number of unlinked genetic loci each comprising linked, nonrecombining sites.
+These methods often struggle to detect multiple divergence times across pairs of
+populations \citep{Oaks2012, Oaks2014reply} or have little information to
+update \textit{a priori} expectations \citep{Oaks2014dpp}.
+More fundamentally, the loss of information inherent to ABC approaches can
+prevent them from discriminating among models
+\citep{Robert2011,Marin2014,Green2015}.
+
+By more efficiently using information from a large number of effectively
+unlinked sites from across the genomes of sampled organisms, the
+full-likelihood Bayesian methods enable more accurate and precise estimates of
+shared divergneces
+\citep{Oaks2018ecoevolity,Oaks2019codemog}.
+
+This raises a question.
+Given a dataset of one or a small number of loci of linked sites,
+is it better to use an ABC approach that correctly models such loci, but
+but suffers from low power and bias?
+Or, is it better to use a full-likelihood approach that has more power,
+but incorrectly assumes the sites in the data are unlinked?
+\jrocomment{Need to flesh out this intro more.}
+
 \section{Methods}
@@
 \ecoevolity.
+
+Ideally, we would have applied both the full-likelihood and ABC methods
+to the datasets simulated using \pymsbayes.
+However, this was not possible, because \dppmsbayes does not store the full
+simulated sequence data, only the population genetic summary statistics used by
+the ABC algorithm.
 
@@
 
+As mentioned in the methods,
+it would have been ideal to apply both the full-likelihood and ABC methods
+to the data simulated via \dppmsbayes.
+Because \dppmsbayes only stores summary statistics from the genetic data, this
+was not possible.
+However, it is unlikely that differences between the simulators implemented in
+\dppmsbayes and \ecoevolity could explain the differences in performance
+between full-likelihood and ABC inference methods.
+Both simulators have been independently validated by suites of tests in the
+\pymsbayes and \ecoevolity distributions.
+Also, the assumption that the simulators are producing nearly identically
+distributed data (barring minor differences in parameterizations between the
+implementations) is supported by our finding that both inference methods
+perform very similarly when the size of the simulated data sets are small
+(i.e., one 500-site locus) and diverge in performance as we increased the size
+of the simulated data sets (\figs \ref{fig:modelerror} \&
+\ref{fig:divtimeerror}).
+
 \section{Acknowledgments}

### 2025-11-26 manuscript/ms.tex
Updating plots of empirical results.

@@
     \begin{center}
-        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-all-pairs/pyco-sumevents-mediterranean-all-pairs-pycoevolity-nevents-cropped.pdf}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-all-pairs/pyco-sumevents-results-comparison-pycoevolity-nevents-cropped.pdf}
         \caption{
-            \Ecoevolity results for all Mediterranean pairs.
+            Results comparison for all Mediterranean pairs.
         }
@@
     \begin{center}
-        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-soil-pairs/pyco-sumevents-mediterranean-soil-pairs-pycoevolity-nevents-cropped.pdf}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/mediterranean-soil-pairs/pyco-sumevents-results-comparison-pycoevolity-nevents-cropped.pdf}
         \caption{
-            \Ecoevolity results for soil Mediterranean pairs.
+            Results comparison for soil Mediterranean pairs.
         }
@@
     \begin{center}
-        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-all-pairs/pyco-sumevents-philippines-all-pairs-pycoevolity-nevents-cropped.pdf}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-all-pairs/pyco-sumevents-results-comparison-pycoevolity-nevents-cropped.pdf}
         \caption{
-            \Ecoevolity results for all Philippines pairs.
+            Results comparison for all Philippines pairs.
         }
@@
     \begin{center}
-        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-negros-panay-pairs/pyco-sumevents-philippines-negros-panay-pairs-pycoevolity-nevents-cropped.pdf}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/empirical-plots/philippines-negros-panay-pairs/pyco-sumevents-results-comparison-pycoevolity-nevents-cropped.pdf}
         \caption{
-            \Ecoevolity results for Negros-Panay pairs.
+            Results comparison for Negros-Panay pairs.
         }
